Hydra Battles and Cie

### 2021-02-11 doc/chapter-powers.tex
Mult index (#28)
* creation of a multiple index

* work on the index

* work on the index

* reorganization of the index (in progress)

\subsection{Correctness Proofs by Reflection}
\label{reflection-section}
\index{coq}{Proof by reflection}
Instead of letting the tactic \texttt{rewrite} look for contexts in which
setoid rewriting is possible, we propose to use (deterministic) computations for
obtaining a ``canonical'' form for terms generated from a variable \texttt{x}
by contructors associated with monoid multiplication and neutral element.

>>>>

\subsection{Correctness Proofs by Reflection}
\label{reflection-section}
\index{coq}{Proofs by reflection}
Instead of letting the tactic \texttt{rewrite} look for contexts in which
setoid rewriting is possible, we propose to use (deterministic) computations for
obtaining a ``canonical'' form for terms generated from a variable \texttt{x}
by contructors associated with monoid multiplication and neutral element.

### 2021-02-11 doc/hydras.tex
work on the index
Mult index (#28)
* creation of a multiple index

* work on the index

* work on the index

* reorganization of the index (in progress)

%\SetWatermarkLightness{0.8}
\definecolor{lightorange}{rgb}{1,0.7,0.5}
\SetWatermarkScale{0.35}
\SetWatermarkText{Work in Progress}
\SetWatermarkColor{lightorange}

@@

% \begin{todo}
%  Still very incomplete!
% \end{todo}

@@

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Main types and type classes}
\begin{tabular}{|c|c|c|l|}
\hline
Name & Description& Page \\\hline
Battle & type class of battle types & \pageref{types:Battle} \\
E0 & (well formed) ordinals below $\epsilon_0$ & \pageref{types:E0}\\
Hvariant & variants for proving termination of hydra battles & \pageref{sect:hvariant-def} \\
Hydra & tree-like representation of hydras & \pageref{types:Hydra} \\
Hydrae & finite sequences of hydras & \pageref{types:Hydrae} \\
ON & ordinal  notations & \pageref{types:ON} \\
ON\_for & comparison of an ordinal notation with Schütte's model &  \pageref{types:ON-for}\\
ON\_iso & isomorphism of ordinal notations  & \pageref{types:ON-iso}\\

ppT1 & pretty printed version of T1 & \pageref{types:ppT1} \\
SubON & comparison of ordinal notations & \pageref{types:SubON} \\
T1 & ordinal terms below $\epsilon_0$ & \pageref{types:T1} \\
T2 & ordinal terms below $\Gamma_0$ & \pageref{types:T2} \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

>>>>

%\SetWatermarkLightness{0.8}
% \definecolor{lightorange}{rgb}{1,0.7,0.5}
% \SetWatermarkScale{0.35}
% \SetWatermarkText{Work in Progress}
% \SetWatermarkColor{lightorange}

@@

% \begin{todo}
%  Still very incomplete!
% \end{todo}
{\Large \textbf{In progress} This index is currently under reorganization for a few days. We aplologize for its incompleteness! }

@@

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Main types and type classes}
\begin{tabular}{|c|c|c|l|}
\hline
Name & Description& Page \\\hline
ppT1 & pretty printed version of T1 & \pageref{types:ppT1} \\
T1 & ordinal terms below $\epsilon_0$ & \pageref{types:T1} \\
T2 & ordinal terms below $\Gamma_0$ & \pageref{types:T2} \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

### 2021-02-11 doc/part-hydras.tex
Mult index (#28)
* creation of a multiple index

* work on the index

* work on the index

* reorganization of the index (in progress)

@@

\index{hydras}{Predicates!round\_n}

\begin{Coqsrc}
Definition round_n n h h' := R1 h h' \/ R2 n h h'.  
\end{Coqsrc}

@@

\index{hydras}{Predicates!round}
\label{sect:infix-round}
\begin{Coqsrc}
Definition round h h' := exists n,  round_n n h h'.

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}
\label{types:Battle}

@@

\index{hydras}{Predicates!Termination}

@@

\begin{Coqsrc}
Class Hvariant {A:Type}{Lt:relation A}(Wf: well_founded Lt)(B : Battle)
  (m: Hydra -> A):   Prop :=
  {variant_decr :forall i h h',
      h <> head ->
      battle_r  B i  h h' -> Lt (m h') (m h)}.
\end{Coqsrc}

@@

\label{types:ON}

@@

If \texttt{OB} is presumed to be correct, the we can consider that \texttt{OA} ``inherits'' its correcteness from the bigger notation system \texttt{OB}.

\label{types:SubON}

@@

\label{types:ON-for}

@@

@@

\label{types:ppT1}
\index{hydras}{Functions!pp@ pp (pretty printing terms in Cantor normal form)}

@@

\label{sect:E0-def}
\label{types:E0}

@@

\index{hydras}{Predicates!path\_to}
\label{sect:path-to-def}

@@

\index{hydras}{Predicates!mlarge @ mlarge (minimal large sequences)}
\begin{Coqsrc}
Definition mlarge alpha (s:list nat) := path_to zero s alpha.
\end{Coqsrc}

@@

\index{maths}{Ordinal numbers!Additive principal ordinals}
\index{hydras}{Library Schutte!AP@AP (additive principal ordinals)}

@@

\index{maths}{Ordinal numbers!Critical ordinals}
\index{hydras}{Library Scutte!Cr@Cr (critical ordinals)}

@@

\index{maths}{Ordinal numbers!Cantor normal form}
\index{hydras}{Library Schutte!Predicates!is\_cnf\_of@is\_cnf\_o (to be a Cantor normal form}

>>>>

\index{hydras}{Library Hydra!Types!Hydra}
\index{hydras}{Library Hydra!Types!Hydrae}

@@

\index{hydras}{Library Hydra!Predicates!round\_n}
\begin{Coqsrc}
Definition round_n n h h' := R1 h h' \/ R2 n h h'.  
\end{Coqsrc}

@@

\index{hydras}{Library Hydra!Predicates!round}
\label{sect:infix-round}
\begin{Coqsrc}
Definition round h h' := exists n,  round_n n h h'.

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}
\label{types:Battle}
\index{hydras}{Library Hydra!Type classes!Battle}

@@

\index{hydras}{Library Hydra!Predicates!Termination}

@@

\index{hydras}{Library Hydra!Type classes!Hvariant}
\begin{Coqsrc}
Class Hvariant {A:Type}{Lt:relation A}(Wf: well_founded Lt)(B : Battle)
  (m: Hydra -> A):   Prop :=
  {variant_decr :forall i h h',
      h <> head ->
      battle_r  B i  h h' -> Lt (m h') (m h)}.
\end{Coqsrc}

@@

\label{types:ON}
\index{hydras}{Library OrdinalNotations!Type classes!ON}

@@

If \texttt{OB} is presumed to be correct, the we can consider that \texttt{OA} ``inherits'' its correctness from the bigger notation system \texttt{OB}.

\label{types:SubON}
\index{hydras}{Library OrdinalNotations!Type classes!SunON}

@@

\label{types:ON-for}
\index{hydras}{Library OrdinalNotations}{Type classes!ON\_correct}

@@

\index{hydras}{Library OrdinalNotations!Type classes!ON\_Iso}

@@

\label{types:ppT1}
\index{hydras}{Library Epsilon0!Functions!pp@ pp (pretty printing terms in Cantor normal form)}

@@

\label{sect:E0-def}
\label{types:E0}
\index{hydras}{Library Epsilon0!Types!E0}

@@

\index{hydras}{Library Epsilon0!Predicates!path\_to}
\label{sect:path-to-def}

@@

\index{hydras}{Library Epsilon0!Predicates!mlarge@mlarge (minimal large sequences)}
\begin{Coqsrc}
Definition mlarge alpha (s:list nat) := path_to zero s alpha.
\end{Coqsrc}

@@

\index{maths}{Ordinal numbers!Additive principal ordinals}
\index{hydras}{Library Schutte!Predicates!AP@AP (additive principal ordinals)}

@@

\index{maths}{Ordinal numbers!Critical ordinals}
\index{hydras}{Library Schutte!Predicates!Cr@Cr (critical ordinals)}

@@

\index{maths}{Ordinal numbers!Cantor normal form}
\index{hydras}{Library Schutte!Predicates!is\_cnf\_of@is\_cnf\_of (to be a Cantor normal form of}
